\thesistitle

### 2019-07-18 sections/background.tex
Finalized the table

\section{Defining clones}

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Symbol} & \textbf{Meaning} & \textbf{Description} & \textbf{Contents} & \textbf{Properties} \\ \midrule
\rowcolor[HTML]{EFEFEF}
S & Clone class collection & \begin{tabular}[c]{@{}l@{}}All clone classes that have been \\ found for a certain software project.\end{tabular} & Set of clone classes & - \\
C & Clone class & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations.\end{tabular} & Set of clone instances & - \\
\rowcolor[HTML]{EFEFEF}
I & Clone instance & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & Set of cloned nodes & \begin{tabular}[c]{@{}l@{}}File (F): The file in which this\\ clone instance is found.\\ Range (R): The range this clone\\ instance spans.\end{tabular} \\
N & Node & \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & Set of tokens. & \begin{tabular}[c]{@{}l@{}}Range (R): The range this node\\ spans.\end{tabular} \\
\rowcolor[HTML]{EFEFEF}
t & Token & \begin{tabular}[c]{@{}l@{}}Smallest relevant entity of a\\ program.\end{tabular} & - & \begin{tabular}[c]{@{}l@{}}Range (R): The range this token \\ spans.\\ Category: Identifier, Keyword, \\ Literal, Separator, Operator,\\ Comment or Whitespace\end{tabular} \\ \bottomrule
\end{tabular}%
}
\caption{Clone related terminology and how it maps to the source code.}
\label{tab:clone-terminology}
\end{table}

>>>>

\section{Defining clones}
Many studies present different definitions for code clone concepts. For this study, we mainly use the definitions from Bruntink et al. \cite{bruntink2005use}, Roy et al. \cite{roy2007survey} and \cite{jiang2007deckard}. We created a summary of these concepts, which can be found in table \ref{tab:clone-terminology}.

\begin{table}[H]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}llll@{}}
\toprule
\rowcolor[HTML]{FFFFFF}
\textbf{Symbol} & \textbf{Meaning} & \textbf{Description} & \textbf{Properties} \\ \midrule
\rowcolor[HTML]{EFEFEF}
S & \begin{tabular}[c]{@{}l@{}}Clone class\\ collection\end{tabular} & \begin{tabular}[c]{@{}l@{}}All clone classes that have been\\found for a certain software\\project.\end{tabular} & \textbf{Clones:} Set of clone classes. \\
\rowcolor[HTML]{FFFFFF}
C & Clone class & \begin{tabular}[c]{@{}l@{}}A set of similar code fragments in\\ different locations.\end{tabular} & \textbf{Instances:} Set of clone instances. \\
\rowcolor[HTML]{EFEFEF}
I & \begin{tabular}[c]{@{}l@{}}Clone\\ instance\end{tabular} & \begin{tabular}[c]{@{}l@{}}A code fragment that appears in\\ multiple locations.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Contents:} Totally ordered set of nodes, ordered\\by their begin positions.\\ \textbf{File:} The file in which this clone instance is \\ found.\\ \textbf{Range:} The range this clone instance spans.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
N & Node & \begin{tabular}[c]{@{}l@{}}A statement or declaration in a \\ codebase.\end{tabular} & \textbf{Range:} The range this node spans. \\
\rowcolor[HTML]{EFEFEF}
R & Range & A part of a source code file. & \begin{tabular}[c]{@{}l@{}}\textbf{Tokens:} Set of tokens that this range spans.\\ \textbf{Begin line/column:} The line and column at \\ which the range starts.\\ \textbf{End line/column:} The line and column at\\ which the range end.\end{tabular} \\
\rowcolor[HTML]{FFFFFF}
T & Token & \begin{tabular}[c]{@{}l@{}}Tokens are the basic lexical\\ building blocks of source code. \\ For this study, this is the smallest\\ relevant entity of a program.\end{tabular} & \begin{tabular}[c]{@{}l@{}}\textbf{Range:} The range this token spans.\\ \textbf{Category:} Identifier, Keyword, Literal, Separator, \\ Operator, Comment or Whitespace\end{tabular} \\ \bottomrule
\end{tabular}%
}
\caption{Clone related terminology and how it maps to the source code.}
\label{tab:clone-terminology}
\end{table}
